FinalManuscript_DISCS_UG

### 2018-06-25 parts/01_introduction_03objectives.tex
Finished ch1

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{opencv_library} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processsing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a plug-in for OpenCV to allow for convenient use of these homomorphic encryption schemes.
\end{enumerate}

>>>>

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{opencv_library} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}
